\documentclass[a4paper,11pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
%\usepackage{fontspec}
%\setmainfont[Ligatures=TeX]{XITS}
\usepackage{newcent}
\usepackage{color}
\DeclareUnicodeCharacter{00A0}{ }
\topmargin=-1.0in % Moves the top of the document 1 inch above the default
\textheight=9.2in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-9pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa
\date{}
\begin{document}
% If you want headings on subsequent pages,
% remove the ``%'' on the next line:
% \pagestyle{headings}
%\fontfamily{qcs}\selectfont
\begin{letter}{\bf{Re: Data Scientist}}
\address{Nets \\Fraud Issuing \& \\Dispute Centre Of Excellence}
%\begin{letter}{\bf{Quantitative Developer Position}}
%\address{DONG energy \\
%Distribution & Customer Solutions }

\begin{flushleft}
Marek Chojnacki \\ % Your name
%Howitzvej 67 G, 1 TV \\
%2000 Frederiksberg \\
mark.chojnacki@gmail.com \\
+45 28834620
\end{flushleft}
\opening{Dear Mr Jacobsen}
I read about the job opening of the `Data Scientist' on the Nets website with interest
because I think it is a great opportunity for me to change my career path and move from academia to business.
I believe my skills, knowledge, and experience make me the suitable candidate for the role.
\vspace{0.15cm}	
\newline
For the last ten years, I have been working for `A Large Ion Collider Experiment (ALICE)', which is situated at the `Large Hadron Collider (LHC)'.
I was a master's student at the Warsaw University of Technology and then a Ph.D. student at Utrecht University. 
Currently, \mbox{I am} a postdoctoral research scientist at the Niels Bohr Institute (NBI) in Copenhagen.
\vspace{0.15cm}	
\newline
During my career, I have gained vast experience in programming (mainly in C++/Linux with Git and SVN as version control systems) 
by developing programs and scripts for complex data analyses on a daily basis.
In my work, I have been using statistical analysis to develop complex algorithms and uncover hidden patterns in data.
Many times, I understood puzzling experimental observations by formulating and implementing mathematical models, that explained those findings.
Moreover, I have also used other programming languages and software frameworks (i.e. bash, Python, Git, Java, MatLab, and SQL). 
I thrive on learning new mathematical methods and software frameworks, and I do it fast.
\vspace{0.15cm}
\newline
I have been cooperating with other members of the collaboration from institutes all over the world.
That requires me to participate in few video meetings per week and give updates of my work. 
Furthermore, I have given presentations at several international conferences.
\vspace{0.15cm}	
\newline
I take responsibility for projects, and my primary concerns are always quality and timeliness.
I am always determined to understand problems and find solutions.
I like working under pressure and seeing that someone is waiting for results. 
At the same time, I do not give unrealistic deadlines.
I enjoy exchanging knowledge in discussions and sharing my findings with others.
%I think those features make me suitable for the position.
\vspace{0.15cm}	
\newline
I believe it is crucial to have a friendly atmosphere in the workplace.
I always try to take part in social activities at work.
During my stay at NBI, I have participated in the DHL relay and prepared food for Christmas lunches.
\vspace{0.15cm}	
\newline
I am sure that my skills, knowledge, and expertise, make me the right candidate for the role.
I know that Nets is the place for me, the place where I will be able to develop.
\vspace{0.15cm}	
\newline
I look forward to hearing from you.
\begin{flushleft}
Yours sincerely,
\\\it{Marek Chojnacki}
\end{flushleft}
\end{letter}
\end{document}